---
title: "Subect87"
output: html_document
---

sandbox for running the SNP pipeline on individual subjects to check

```{r}
library(tidyverse)
source("../MAP_functions.R")
library(tidyquant)
library(GGally)
```

```{r}
subject_id = 87
rare_cutoff = 3
cov_cutoff = 10
```


```{r}
print(paste("SUBJECT_ID is",subject_id))
  
  library(tidyverse)
  source("../MAP_functions.R")
  library(assertthat)
  #load Pos_count
  #rare_cutoff <- 3
  Pos_count <- read_delim("../Pos_count.tsv", show_col_types = FALSE)
  assert_that(nrow(Pos_count) > 0)
  rare_iSNPs <- Pos_count %>% filter(n<=rare_cutoff) %>%
    .$Position
  common_iSNPs <- Pos_count %>% filter(n>rare_cutoff) %>%
    .$Position
  num_rare = length(rare_iSNPs)
  num_common = length(common_iSNPs)
  print(paste("Rare iSNP cutoff = ",rare_cutoff))
  print(paste("num rare iSNPs = ",num_rare))
  print(paste("num common iSNPs = ",num_common))
  
  #load recomb_coords - recombination blocks cutoffs = 1
  fastgear_fiji_recombs <- read.delim("~/GitHub/Ct_MAP_analysis/fastgear_fiji_recombs") %>%
    select(Start,End,...1,...2,...3)
  print("Recombination block cutoff = 3")
  assert_that(nrow(fastgear_fiji_recombs) > 0)
  colnames(fastgear_fiji_recombs) <- c("Start","End","c1","c2","c3")
  R_name = paste0(subject_id,"R")
  V_name = paste0(subject_id,"V")
  C_name = paste0(subject_id,"C")
  C_recomb <- recomb_coords(fastgear_fiji_recombs,C_name)
  R_recomb <- recomb_coords(fastgear_fiji_recombs,R_name)
  V_recomb <- recomb_coords(fastgear_fiji_recombs,V_name)
  C_recomb_bases <- length(C_recomb)
  R_recomb_bases <- length(R_recomb)
  V_recomb_bases <- length(V_recomb)
  print(paste("Num bases in C recomb blocks= ",C_recomb_bases))
  print(paste("Num bases in R recomb = blocks",R_recomb_bases))
  print(paste("Num bases in V recomb = blocks",V_recomb_bases))
  
  # load SNPs from MAP analysis (NOTE cutoff cov=10)
  #cov_cutoff = 10
  print(paste("Coverage cutoff = ",cov_cutoff))
  R_MAP <- read_MAP(paste0("~/Documents/2021-Fiji-Ct_paper/MAP_results/MAP_files/",subject_id,"R_MAP.txt"),"R") %>%
    filter(regular > -1 & regular < 1) %>%
    filter(Coverage > cov_cutoff) %>%
    select(Position,SNP_percent)
  assert_that(nrow(R_MAP) > 0)
  R_bases <- nrow(R_MAP)
  print(paste("Numbers of R bases above cutoff is ",R_bases))
  C_MAP <- read_MAP(paste0("~/Documents/2021-Fiji-Ct_paper/MAP_results/MAP_files/",subject_id,"C_MAP.txt"),"C") %>%
    filter(regular > -1 & regular < 1) %>%
    filter(Coverage > cov_cutoff) %>%
    select(Position,SNP_percent)
  assert_that(nrow(C_MAP) > 0)
  C_bases <- nrow(C_MAP)
  print(paste("Numbers of C bases above cutoff is ",C_bases))
  V_MAP <- read_MAP(paste0("~/Documents/2021-Fiji-Ct_paper/MAP_results/MAP_files/",subject_id,"V_MAP.txt"),"V") %>%
    filter(regular > -1 & regular < 1) %>%
    filter(Coverage > cov_cutoff) %>%
    select(Position,SNP_percent)
  assert_that(nrow(V_MAP) > 0)
  V_bases <- nrow(V_MAP)
  print(paste("Numbers of V bases above cutoff is ", V_bases))
  
# Join all 3 together and parse out the rare sites (ie < 90% in any of the 3)  
  Total_iSNPs <- inner_join(R_MAP,V_MAP, by = "Position") %>%
    inner_join(.,C_MAP, by = "Position") %>%
    filter(!(SNP_percent.x > 90 & SNP_percent.y > 90 & SNP_percent > 90)) %>%
    mutate(SNP = case_when(
      Position %in% rare_iSNPs ~ "rare_iSNP",
      Position %in% common_iSNPs ~ "common_iSNP",
      TRUE ~ "other_SNP"
    )) %>%
    mutate(fastGEAR = ifelse(Position %in% c(R_recomb,C_recomb,V_recomb),"fastGEAR_block","other")) %>%
    add_column(subject_id = subject_id)
  colnames(Total_iSNPs) <- c("Position","R_percent","V_percent","C_percent","SNP","fastGEAR_block", "subject_id")
  outfile2 <- paste0("./iSNPs_by_subject/iSNPs_subject_",subject_id,".tsv")
 # write_tsv(Total_iSNPs,outfile2)
  assert_that(nrow(Total_iSNPs) > 0)
  print(paste("Number of iSNP positions = ",nrow(Total_iSNPs)))
  
  # R only fixed SNPs
  RonlyF <- Total_iSNPs %>%
    filter(R_percent < 10 & V_percent >= 90 & C_percent >= 90) %>%
    nrow()
  RonlyFrare <- Total_iSNPs %>%
    filter(R_percent < 10 & V_percent >= 90 & C_percent >= 90) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  RonlyFrecomb <- Total_iSNPs %>%
    filter(R_percent < 10 & V_percent >= 90 & C_percent >= 90) %>%
    filter(fastGEAR_block == "fastGEAR_block") %>%
    nrow()
  print(paste("R only fixed SNPs (RonlyF) = ",RonlyF))
  print(paste("R only rare fixed SNPs (RonlyFrare) = ",RonlyFrare))
  print(paste("R only fixed SNPs in recombinant regions (RonlyFrecomb) = ",RonlyFrecomb))
  
  #R only iSNPs
  RonlyRI <- Total_iSNPs %>%
    filter(R_percent >= 10 & R_percent < 90 & V_percent >= 90 & C_percent >= 90) %>%
    nrow()
  RonlyRIrare <- Total_iSNPs %>%
    filter(R_percent >= 10 & R_percent < 90 & V_percent >= 90 & C_percent >= 90) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  RonlyRIrecomb <- Total_iSNPs %>%
    filter(R_percent >= 10 & R_percent < 90 & V_percent >= 90 & C_percent >= 90) %>%
    filter(fastGEAR_block == "fastGEAR_block") %>%
    nrow()
  print(paste("R only iSNPs (RonlyRI) = ",RonlyRI))
  print(paste("R only rare iSNPs (RonlyRIrare) = ",RonlyRIrare))
  print(paste("R only iSNPs in recombinant regions (RonlyRIrecomb) = ",RonlyRIrecomb))
  
  #C only fixed
  ConlyF <-  Total_iSNPs %>%
    filter(C_percent < 10 & V_percent >= 90 & R_percent >= 90) %>%
    nrow()
  ConlyFrare <- Total_iSNPs %>%
    filter(C_percent < 10 & V_percent >= 90 & R_percent >= 90) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  ConlyFrecomb <- Total_iSNPs %>%
    filter(C_percent < 10 & V_percent >= 90 & R_percent >= 90) %>%
    filter(fastGEAR_block == "fastGEAR_block") %>%
    nrow()
  print(paste("C only fixed SNPs (ConlyF) = ",ConlyF))
  print(paste("C only rare fixed SNPs (ConlyFrare) = ",ConlyFrare))
  print(paste("C only fixed SNPs in recombinant regions (ConlyFrecomb) = ",ConlyFrecomb))
  
  #C only iSNPs
  ConlyRI <- Total_iSNPs %>%
    filter(C_percent >= 10 & C_percent < 90 & V_percent >= 90 & R_percent >= 90) %>%
    nrow()
  ConlyRIrare <- Total_iSNPs %>%
    filter(C_percent >= 10 & C_percent < 90 & V_percent >= 90 & R_percent >= 90) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  ConlyRIrecomb <- Total_iSNPs %>%
    filter(C_percent >= 10 & C_percent < 90 & V_percent >= 90 & R_percent >= 90) %>%
    filter(fastGEAR_block == "fastGEAR_block") %>%
    nrow()
  print(paste("C only iSNPs (ConlyRI) = ",ConlyRI))
  print(paste("C only rare iSNPs (ConlyRIrare) = ",ConlyRIrare))
  print(paste("C only iSNPs in recombinant regions (ConlyRIrecomb) = ",ConlyRIrecomb))
  
  #V only fixed
  VonlyF <- Total_iSNPs %>%
    filter(V_percent < 10 & C_percent >= 90 & R_percent >= 90) %>%
    nrow()
  VonlyFrare <- Total_iSNPs %>%
    filter(V_percent < 10 & C_percent >= 90 & R_percent >= 90) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  VonlyFrecomb <- Total_iSNPs %>%
    filter(V_percent < 10 & C_percent >= 90 & R_percent >= 90) %>%
    filter(fastGEAR_block == "fastGEAR_block") %>%
    nrow()
  print(paste("V only fixed SNPs (VonlyF) = ",VonlyF))
  print(paste("V only rare fixed SNPs (VonlyFrare) = ",VonlyFrare))
  print(paste("V only fixed SNPs in recombinant regions (VonlyFrecombb) = ",VonlyFrecomb))
  
  #V only iSNPs
  VonlyRI <- Total_iSNPs %>%
    filter(V_percent >= 10 & V_percent < 90 & C_percent >= 90 & R_percent >= 90) %>%
    nrow()
  VonlyRIrare <- Total_iSNPs %>%
    filter(V_percent >= 10 & V_percent < 90 & C_percent >= 90 & R_percent >= 90) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  VonlyRIrecomb <- Total_iSNPs %>%
    filter(V_percent >= 10 & V_percent < 90 & C_percent >= 90 & R_percent >= 90) %>%
    filter(fastGEAR_block == "fastGEAR_block") %>%
    nrow()
  print(paste("V only iSNPs (VonlyRI) = ",VonlyRI))
  print(paste("V only rare iSNPs (VonlyRIrare) = ",VonlyRIrare))
  print(paste("V only iSNPs in recombinant regions (VonlyRIrecomb) = ",VonlyRIrecomb))
  
  #RC only fixed
  RConlyF <- Total_iSNPs %>%
    filter(V_percent >= 90 & C_percent < 10 & R_percent < 10) %>%
    nrow()
  RConlyFrare <- Total_iSNPs %>%
    filter(V_percent >= 90 & C_percent < 10 & R_percent < 10) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  RConlyFrecomb <- Total_iSNPs %>%
    filter(V_percent >= 90 & C_percent < 10 & R_percent < 10) %>%
    filter(fastGEAR_block == "fastGEAR_block") %>%
    nrow()
  print(paste("RC only fixed SNPs (RConlyF) = ",RConlyF))
  print(paste("RC only rare fixed SNPs (RConlyFrare) = ",RConlyFrare))
  print(paste("RC only fixed SNPs in recombinant regions (RConlyFrecomb) = ",RConlyFrecomb))
  
  #RC only iSNPs
  RConlyRI <- Total_iSNPs %>%
    filter(V_percent >= 90 & C_percent >= 10 & C_percent < 90 & R_percent >= 10 & R_percent < 90) %>%
    nrow()
  RConlyRIrare <- Total_iSNPs %>%
    filter(V_percent >= 90 & C_percent >= 10 & C_percent < 90 & R_percent >= 10 & R_percent < 90) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  RConlyRIrecomb <- Total_iSNPs %>%
    filter(V_percent >= 90 & C_percent >= 10 & C_percent < 90 & R_percent >= 10 & R_percent < 90) %>%
    filter(fastGEAR_block == "fastGEAR_block") %>%
    nrow()
  print(paste("RC only iSNPs (RConlyRI) = ",RConlyRI))
  print(paste("RC only rare iSNPs (RConlyRIrare) = ",RConlyRIrare))
  print(paste("RC only iSNPs in recombinant regions (RConlyRIrecomb) = ",RConlyRIrecomb))
  
  #RV only fixed
  RVonlyF <- Total_iSNPs %>%
    filter(C_percent >= 90 & V_percent < 10 & R_percent < 10) %>%
    nrow()
  RVonlyFrare <- Total_iSNPs %>%
    filter(C_percent >= 90 & V_percent < 10 & R_percent < 10) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  RVonlyFrecomb <- Total_iSNPs %>%
    filter(C_percent >= 90 & V_percent < 10 & R_percent < 10) %>%
    filter(fastGEAR_block == "fastGEAR_block") %>%
    nrow()
  print(paste("RV only fixed SNPs (RVonlyF) = ",RVonlyF))
  print(paste("RV only rare fixed SNPs (RVonlyFrare) = ",RVonlyFrare))
  print(paste("RV only fixed SNPs in recombinant regions (RVonlyFrecomb) = ",RVonlyFrecomb))
  
  #RV only iSNPs
  RVonlyRI <- Total_iSNPs %>%
    filter(C_percent >= 90 & V_percent >= 10 & V_percent < 90 & R_percent >= 10 & R_percent < 90) %>%
    nrow()
  RVonlyRIrare <- Total_iSNPs %>%
    filter(C_percent >= 90 & V_percent >= 10 & V_percent < 90 & R_percent >= 10 & R_percent < 90) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  RVonlyRIrecomb <- Total_iSNPs %>%
    filter(C_percent >= 90 & V_percent >= 10 & V_percent < 90 & R_percent >= 10 & R_percent < 90) %>%
    filter(fastGEAR_block == "fastGEAR_block") %>%
    nrow()
  print(paste("RV only iSNPs (RVonlyRI) = ",RVonlyRI))
  print(paste("RV only rare iSNPs (RVonlyRIrare) = ",RVonlyRIrare))
  print(paste("RV only iSNPs in recombinant regions (RVonlyRIrecomb) = ",RVonlyRIrecomb))
  
  #VC only fixed
  VConlyF <- Total_iSNPs %>%
    filter(R_percent >= 90 & V_percent < 10 & C_percent < 10) %>%
    nrow()
  VConlyFrare <- Total_iSNPs %>%
    filter(R_percent >= 90 & V_percent < 10 & C_percent < 10) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  VConlyFrecomb <- Total_iSNPs %>%
    filter(R_percent >= 90 & V_percent < 10 & C_percent < 10) %>%
    filter(fastGEAR_block == "fastGEAR_block") %>%
    nrow()
  print(paste("VC only fixed SNPs (VConlyF) = ",VConlyF))
  print(paste("VC only rare fixed SNPs (VConlyFrare) = ",VConlyFrare))
  print(paste("VC only fixed SNPs in recombinant regions (VConlyFrecomb) = ",VConlyFrecomb))
  
  #VC only iSNPs
  VConlyRI <- Total_iSNPs %>%
    filter(R_percent >= 90 & V_percent >= 10 & V_percent < 90 & C_percent >= 10 & C_percent < 90) %>%
    nrow()
  VConlyRIrare <- Total_iSNPs %>%
    filter(R_percent >= 90 & V_percent >= 10 & V_percent < 90 & C_percent >= 10 & C_percent < 90) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  VConlyRIrecomb <- Total_iSNPs %>%
    filter(R_percent >= 90 & V_percent >= 10 & V_percent < 90 & C_percent >= 10 & C_percent < 90) %>%
    filter(fastGEAR_block == "fastGEAR_block") %>%
    nrow()
  print(paste("VC only iSNPs (VConlyRI) = ",VConlyRI))
  print(paste("VC only rare iSNPs (VConlyRIrare) = ",VConlyRIrare))
  print(paste("VC only iSNPs in recombinant regions (VConlyRIrecomb) = ",VConlyRIrecomb))
  
  #all_fixed
  AllF <- Total_iSNPs %>%
    filter(R_percent <10 & V_percent < 10 & C_percent < 10) %>%
    nrow()
  AllFrare <- Total_iSNPs %>%
    filter(R_percent <10 & V_percent < 10 & C_percent < 10) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  AllFrecomb <- Total_iSNPs %>%
    filter(R_percent <10 & V_percent < 10 & C_percent < 10) %>%
    filter(fastGEAR_block == "fastGEAR_block") %>%
    nrow()
  print(paste("All fixed SNPs (AllF) = ",AllF))
  print(paste("All rare fixed SNPs (AllFrare) = ",AllFrare))
  print(paste("All fixed SNPs in recombinant regions (AllFrecomb) = ",AllFrecomb))
  
  #all iSNPs
  AllRI <- Total_iSNPs %>%
    filter(R_percent >= 10 & R_percent < 90 & V_percent >= 10 & V_percent < 90 & C_percent >= 10 & C_percent < 90) %>%
    nrow()
  AllRIrare <- Total_iSNPs %>%
    filter(R_percent >= 10 & R_percent < 90 & V_percent >= 10 & V_percent < 90 & C_percent >= 10 & C_percent < 90) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  AllRIrecomb <- Total_iSNPs %>%
    filter(R_percent >= 10 & R_percent < 90 & V_percent >= 10 & V_percent < 90 & C_percent >= 10 & C_percent < 90) %>%
    filter(fastGEAR_block == "fastGEAR_block") %>%
    nrow()
  print(paste("All iSNPs (AllRI) = ",AllRI))
  print(paste("All rare  iSNPs (AllRIrare) = ",AllRIrare))
  print(paste("All iSNPs in recombinant regions (AllRIrecomb) = ",AllRIrecomb))
  
  #fixed in one compartment, intermediate in others
  
  RonlyF_VIrare <- Total_iSNPs %>%
    filter(R_percent < 10 & V_percent >= 10 & V_percent < 90 & C_percent >= 90) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  
  RonlyF_CIrare <- Total_iSNPs %>%
    filter(R_percent < 10 & C_percent >= 10 & C_percent < 90 & V_percent >= 90) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  
  RonlyF_CandVIrare <- Total_iSNPs %>%
    filter(R_percent < 10 & C_percent >= 10 & C_percent < 90 & V_percent >= 10 & V_percent < 90) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  
  ConlyF_VIrare <- Total_iSNPs %>%
    filter(C_percent < 10 & V_percent >= 10 & V_percent < 90 & R_percent >= 90) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  
  ConlyF_RIrare <- Total_iSNPs %>%
    filter(C_percent < 10 & R_percent >= 10 & R_percent < 90 & V_percent >= 90) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  
  ConlyF_RandVIrare <- Total_iSNPs %>%
    filter(C_percent < 10 & R_percent >= 10 & R_percent < 90 & V_percent >= 10 & V_percent < 90) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  
  VonlyF_RIrare <- Total_iSNPs %>%
    filter(V_percent < 10 & R_percent >= 10 & R_percent < 90 & C_percent >= 90) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  
  VonlyF_CIrare <- Total_iSNPs %>%
    filter(V_percent < 10 & C_percent >= 10 & C_percent < 90 & R_percent >= 90) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  
  VonlyF_CandRIrare <- Total_iSNPs %>%
    filter(V_percent < 10 & R_percent >= 10 & R_percent < 90 & C_percent >= 10 & C_percent < 90) %>%
    filter(SNP == "other_SNP" | SNP == "rare_iSNP") %>%
    nrow()
  
  print(paste("R is fixed, V only is intermediate, and rare (RonlyF_VIrare) = ",RonlyF_VIrare))
  print(paste("R is fixed, C only is intermediate, and rare (RonlyF_CIrare) = ",RonlyF_CIrare))
  print(paste("R is fixed, V and C are intermediate, and rare (RonlyF_CandVIrare) = ",RonlyF_CandVIrare))
  print(paste("C is fixed, V only is intermediate, and rare (ConlyF_VIrare) = ",ConlyF_VIrare))
  print(paste("C is fixed, R only is intermediate, and rare (ConlyF_RIrare) = ",ConlyF_RIrare))
  print(paste("C is fixed, R and V are intermediate, and rare (ConlyF_RandVIrare) = ",ConlyF_RandVIrare))
  print(paste("V is fixed, C only is intermediate, and rare (VonlyF_CIrare) = ",VonlyF_CIrare))
  print(paste("V is fixed, R only is intermediate, and rare (VonlyF_RIrare) = ",VonlyF_RIrare))
  print(paste("V is fixed, R and C are intermediate, and rare (VonlyF_CandRIrare) = ",VonlyF_CandRIrare))
  
```



```{r}
ggparcoord(data = Total_iSNPs,
           columns = 2:4,
           scale = "globalminmax",
           alphaLines = 0.2) 
```


# denovo SNPs

```{r}
T1T2_denovo_snps <- read_lines("../T1T2_snps_denovo_v2.list")
  
  T1T2_denovo_df <- full_join(R_MAP,V_MAP, by = "Position") %>%
    full_join(.,C_MAP, by = "Position") %>%
    filter(Position %in% T1T2_denovo_snps)
  colnames(T1T2_denovo_df) <- c("Position","Rectum","Vagina","Endocervix")
  
  T1T2_denovo_df_long <- gather(T1T2_denovo_df,"Body_site","SNP_percent",-Position)
```

```{r}
ggparcoord(data = T1T2_denovo_df,
             columns = 2:4,
             scale = "globalminmax",
             alphaLines = 0.2,
             title = paste0("cDenovo_SNPs for" ,subject_id))
```

```{r}
test_snpplot <- function(test_df,x1=1,x2=1042504,sz = 0.5) {
  library(RColorBrewer)
library(cowplot)
cust_pal <- brewer.pal(3,"Accent")
snps_ref1 <- ggplot(filter(test_df,Body_site == "Endocervix"), aes(x= Position, y= SNP_percent, color = Body_site)) +
    geom_point(alpha = 0.7, size = sz) + 
  scale_color_manual(values = cust_pal[1]) +
    xlim(x1,x2)+
   ylab("% reference") +
    theme_bw()

snps_ref2 <- ggplot(filter(test_df,Body_site == "Rectum"), aes(x= Position, y= SNP_percent, color = Body_site)) +
    geom_point(alpha = 0.7, size = sz) + 
  scale_color_manual(values = cust_pal[2]) +
    xlim(x1,x2)+
    ylab("% reference") +
    theme_bw()

snps_ref3 <- ggplot(filter(test_df,Body_site == "Vagina"), aes(x= Position, y= SNP_percent, color = Body_site)) +
    geom_point(alpha = 0.7, size = sz) + 
  scale_color_manual(values = cust_pal[3]) +
    xlim(x1,x2)+
  ylab("% reference") +
    theme_bw()

plot_grid(snps_ref1,snps_ref2,snps_ref3, ncol = 1, align = 'v')
  
}
```



```{r}
test_snpplot(T1T2_denovo_df_long)
```
 
   
```{r}
ggplot(T1T2_denovo_df_long, aes(x=SNP_percent,color = Body_site)) +
    geom_boxplot() + 
    scale_color_brewer(palette = "Accent") +
    xlab("Percent_cDenovo_reference") +
    ggtitle(paste0("cDenovo reference SNPs for ",subject_id)) +
    theme_bw() +
    theme(axis.text.y = element_blank())
```
  
```{r}
print(paste("Number cDenovo Ref SNPs for C = ",nrow(filter(T1T2_denovo_df,Endocervix > 90))))
  print(paste("Number cDenovo Non-Ref SNPs for C = ",nrow(filter(T1T2_denovo_df,Endocervix < 10))))
  print(paste("Number cDenovo iSNPs for C = ",nrow(filter(T1T2_denovo_df,Endocervix >= 10 & Endocervix <= 90))))
  
  print(paste("Number cDenovo Ref SNPs for R = ",nrow(filter(T1T2_denovo_df,Rectum > 90))))
  print(paste("Number cDenovo Non-Ref SNPs for R = ",nrow(filter(T1T2_denovo_df,Rectum < 10))))
  print(paste("Number cDenovo iSNPs for R = ",nrow(filter(T1T2_denovo_df,Rectum >= 10 & Rectum <= 90))))
  
  print(paste("Number cDenovo Ref SNPs for V = ",nrow(filter(T1T2_denovo_df,Vagina > 90))))
  print(paste("Number cDenovo Non-Ref SNPs for V = ",nrow(filter(T1T2_denovo_df,Vagina < 10))))
  print(paste("Number cDenovo iSNPs for V = ",nrow(filter(T1T2_denovo_df,Vagina >= 10 & Vagina <= 90))))
```
 
  Gubbins predicts several recombination sites in 87R
  
 SEQUENCE	GUBBINS	CDS	54298	58561	0.000	.	0	node="internal_ROOT->internal_5";neg_log_likelihood="368.618680";taxa=" Reference 87R";snp_count="51";
SEQUENCE	GUBBINS	CDS	708153	708196	0.000	.	0	node="internal_ROOT->internal_5";neg_log_likelihood="212.875744";taxa=" Reference 87R";snp_count="11";
SEQUENCE	GUBBINS	CDS	1029469	1031524	0.000	.	0	node="internal_ROOT->internal_5";neg_log_likelihood="169.444676";taxa=" Reference 87R";snp_count="16";
SEQUENCE	GUBBINS	CDS	778800	779493	0.000	.	0	node="internal_ROOT->internal_5";neg_log_likelihood="115.840350";taxa=" Reference 87R";snp_count="6";


```{r}
all_SNPs <- 
 inner_join(R_MAP,V_MAP, by = "Position") %>%
    inner_join(.,C_MAP, by = "Position") 
colnames(all_SNPs) <- c("Position","Rectum","Vagina","Endocervix")
```


```{r}
plotGub <- function(Gubstart,Gubend,subject_id,test_df) {
  test_df %>%
    filter((Position >= Gubstart & Position <=  Gubend)) %>%
    ggparcoord(
             columns = 2:4,
             scale = "globalminmax",
             alphaLines = 0.2,
             title = paste("Subject",subject_id,"coords",Gubstart,"to",Gubend))
}
```

Highest likelihood
54298	58561
```{r}
plotGub(54298,58561,87,all_SNPs)
test_snpplot(T1T2_denovo_df_long,54298,58561,sz=1)
```

I think this might be due to missing data causing these apparent 

```{r}
nrow(filter(R_MAP,Position >= 54298	& Position <= 58561))
nrow(filter(C_MAP,Position >= 54298	& Position <= 58561))
nrow(filter(V_MAP,Position >= 54298	& Position <= 58561))
```


